---
title: "KPMG AU Data Analytics virtual internship"
author: "usman derek yahaya"
date: "24/2/2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Introduction

This is a case study solution for the KPMG Virtual Internship, this
internship covers tasks in Data Quality Assessment, Data Insight, Data
Insight and Presentation.

## Content

1.Background 2.Data Quality Assessment 3.Data Insight 4.Data Insights
and Presentation

### Background

As a data analyst for a medium size bikes & cycling accessories
organisation, Sprocket Central Pty Ltd would like to for me to help
review its customer and transactions data. The organisation has a large
data set relating to its customers and would like for the data analytics
team to analyse it to help optimize its marketing strategy. The team
lead provided me with 3 datasheets:

1.Customer Demographic 2.Customer Addresses 3.Transactions data in the
past 3 months

### Data Quality Assessment

Data Quality Assessment is a process of evaluating data and measuring it
against selected quality criteria such as completeness and validity
(GeeksforGeeks, 2022). therefore our data would have to possess
qualities of a Data Quality Assessment, the following below can be
regarded as characteristics of data quality assessment.

1.  **Accuracy: Error-free or misspellings free**
2.  **Completeness: Free of empty rows/values**
3.  **Consistency: Linking Primary Key**
4.  **Timeliness: Relevant Data with Relevant Time period**
5.  **Relevance: special characters free**
6.  **Validity: The appropriate data type for analysis**
7.  **Uniqueness: Free of duplicate rows/values**

```{r loading packages, echo=FALSE, warning=FALSE}
library(tidyverse)
```

###Retrievng Data Information
```{r data structure}
KPMG_DATA_CustomerAddress <- read_csv("C:/Users/kenne/OneDrive/Desktop/KPMG/KPMG_DATA - CustomerAddress.csv")
KPMG_DATA_CustomerDemographic <- read_csv("C:/Users/kenne/OneDrive/Desktop/KPMG/KPMG_DATA - CustomerDemographic.csv")
KPMG_DATA_Transaction <- read_csv("C:/Users/kenne/OneDrive/Desktop/KPMG/KPMG_DATA - Transaction.csv")

df <- KPMG_DATA_Transaction
Address <- KPMG_DATA_CustomerAddress
Demo <- KPMG_DATA_CustomerDemographic
```

###Data Preview
```{r display data structures}
str(df)
str(Address)
str(Demo)
```


```

### Checking For Missing Values
```{r NA values}
## The transaction data looks to have some missing values
apply(X = is.na(df), MARGIN = 2, FUN = sum)
```
Next we look at the data to review the context behind the missing data and of what repercussion it is to the analysis.
```{r data preview}
str(df)
```
The transactions has less than 1% of transactions (totalling less than 0.1% of revenue) with missing fields. These records can be removed from the database.
```{r remove NA values}
df2 <- df[complete.cases(df), ]
```


```{r}
##Next we combine the customer and demography data

list_df = list(Demo,Address)
customer <- list_df %>% reduce(left_join, by = 'customer_id')

apply(X = is.na(customer), MARGIN = 2, FUN = sum)
```
The customer database also does have missing value, however, key variables to the analysis such as bike related purchases, wealth segement, car owner seem to have required data for analysis. 

However, we are analyzing for australia and as such customers not in the country are dropped.
```{r}
customer <- customer %>% drop_na(country)
```

### Checking Data Type
```{r}
str(customer)
```
```{r}
str(df2)
```
```{r}
## Change customer date of birth in customer data frame from character to date

```

### Summary Statistics
```{r}
## Descriptive Statistics
summary(df)

```

```{r}
summary(customer)
```
### Checking for outliers
```{r}

boxplot(df$list_price,
        ylab = "Price")
```
From the box plot, it doesn't seem to be an outlier. 

```{r}
boxplot(customer$bike_related_purchases,
        ylab = "Purchase")
```

```{r warning=FALSE}
boxplot(customer$tenure,
        ylab = "Tenure")
```

## Data Insight
Here we will go through a series of visualizations.

### Customers Preference by Brand
Here, we plot the count of customers purchase according to the brand
```{r}
ggplot(data = df) +
  geom_bar(mapping = aes(x = brand, fill=brand))
```

###  Preference by Brand
Here, we plot the sales according to the different brands of bikes sold.
```{r}
ggplot(data = df) +
  geom_col(mapping = aes(x = brand, y = list_price, fill=brand))

```

###  Sales by Car Owners
Here, we plot the customer purchase based on whether they own a car or not.
```{r}
ggplot(data = customer) +
  geom_col(mapping = aes(x = owns_car, y = bike_related_purchases, fill=deceased_indicator))
```

###  Customer Wealth Classification according to State.
Here, we plot wealth classification according of customers according to states.
```{r}
ggplot(data = customer) +
  geom_bar(mapping = aes(x = state, fill=wealth_segment))
```

### Data Insight and Presentation

In the final step, we will be delivering our insights and providing recommendations based on our analysis.

Here, we revisit our business questions and share with you our high-level business recommendations.

1. What are the trends identified?

* Majority of customers prefer the solex bike brand as compared to the norco bicycle brand.
* Mass Customer consist of a large number across states in Australia.